|

### 2023-02-08 paper.Rmd
Wed Feb  8 21:00:07 CET 2023: update-remote.sh

Note that the results for the real world symbolic regression problems inside this chapter, except for the airfoil problem (see subsection [Influence on Run-Time]), have not been analyzed for their total run-time. This is due to the fact, that experiments were run on different computers architectures which resulted in strongly biased results.

@@

The results for the median best fitness over the evolutionary search are visualized in figure \@ref(fig:symReg-Fitness). Figure \@ref(fig:symReg-Fitness-BoxPlots) shows the distribution of final fitness values on both the test and training set as box plots.

@@

Table \@ref(tab:full-run-realWorldSymReg-fitness) summarizes the results for the median best fitness achieved after 30 generations and shows the results of computing the statistical tests.

@@

# Create the data frame from csv
df <- read.csv(
  #"/Users/rmn/github/master_thesis/data/summary_table_final_fit_mean.csv",
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit_median.csv",
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character", "character")
)

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "DAE.GP"],4)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df[i, "Pre.Trained_DAE.GP"],4))
    }
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "Pre.Trained_DAE.GP"],4)))
  df_bold[i, "DAE.GP"] <- as.character(round(df[i, "DAE.GP"],4))
  }
}
# shorten column names
col_names <- c("Problem", "Hidden-Layers", "Set", "DAE-GP", "Pre-Trained", "P-Value", "Cliffs-Delta")

@@

>>>>

Note that the results for the real world symbolic regression problems inside this chapter, except for the airfoil problem (see subsection [Influence on Run-Time]), have not been analyzed for their total run-time. This is due to the fact, that experiments were run on different computers architectures which would result in biased results.

@@

@@

The results for the median best fitness over the evolutionary search are visualized in figure \@ref(fig:symReg-Fitness). In general, pre-training and regular DAE-GP both are able to improve on the best fitness found over the evolutionary search. Looking at figure \@ref(fig:symReg-Fitness), it appears that no significant differences for the best fitness between both algorithms exist. Regular DAE-GP achieves a slightly lower RMSE on the test set for Airfoil, Boston Housing and the Energy Cooling dataset while pre-trained DAE-GP is slightly better for the Concrete dataset.

@@

# Create the data frame from csv
df_symreg_fitness <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit_median.csv",
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character", "character")
)

# Create a new dataframe with the modified values of the two columns,
df_bold <- df_symreg_fitness

for(i in 1:nrow(df_symreg_fitness)){
  if(df_symreg_fitness[i, "DAE.GP"] < df_symreg_fitness[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df_symreg_fitness[i, "DAE.GP"],4)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df_symreg_fitness[i, "Pre.Trained_DAE.GP"],4))
    }
  else if (df_symreg_fitness[i, "DAE.GP"] > df_symreg_fitness[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df_symreg_fitness[i, "Pre.Trained_DAE.GP"],4)))
  df_bold[i, "DAE.GP"] <- as.character(round(df_symreg_fitness[i, "DAE.GP"],4))
  }
}
# shorten column names
col_names <- c("Problem", "Hidden-Layers", "Set", "DAE-GP", "Pre-Trained", "P-Value", "Cliffs-Delta")

@@

Table \@ref(tab:full-run-realWorldSymReg-fitness) summarizes the results for the median best fitness achieved after 30 generations and shows the results of computing the statistical tests. As expected after reviewing figure \@ref(fig:symReg-Fitness), none of the differences in median best fitness are statistically significant and pre-training has only a very small, negligible effect strength for Cliff's Delta ranging between `r min(df_symreg_fitness$Cliffs_Delta)` and `r max(df_symreg_fitness$Cliffs_Delta)` [@Vargha2000ACA].

Figure \@ref(fig:symReg-Fitness-BoxPlots) shows the distribution of final fitness values on both the test and training set as box plots. It shows that depending on the symbolic regression problem, the dispersion of fitness values is different for both DAE-GP variants. For example, a comparativley large span is visible for the airfoil problem while fitness scores for Energy Cooling are much more concentrated. The distribution are nontheless similar for both algorithms which does not suggest any meaningful differences between using pre-training and the distribution of final fitness scores.
